Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-02-15 paper_comparison/paper_comparison/paper_comparison.Rmd
use more accurate lang

A conditional expectation is taken because $E$ is designed to be invariant to different realizations of $\boldsymbol{X}$. However, solving this conditional expectation analytically is difficult as $\boldsymbol{X}$ can follow almost any distribution. We make an assumption that $\boldsymbol{X}$ follows a particular multivariate normal distribution, and repeatedly draw samples from the given model $M$. The estimate of $E$ is obtained by taking the average of the $E_{sample}$ calculated for each sample.

>>>>

A conditional expectation is taken because $E$ is designed to be invariant to different realizations of $\boldsymbol{X}$. However, solving this conditional expectation analytically is very difficult as $\boldsymbol{X}$ can follow arbitrary distributions. Therefore, we make an assumption that $\boldsymbol{X}$ follows a particular multivariate normal distribution

We make an assumption that all the realizations of $\boldsymbol{X}$ are generated from a multivariate normal distribution $N(\boldsymbol{0}, 0.3^2\boldsymbol{I})$ and then rescaled by the min-max normalization. The estimate of $E$ is obtained by taking the average of the $E_{sample}$ calculated for samples drawn from the given model $M$ repeatedly.

### 2023-02-15 paper_comparison/paper_comparison/paper_comparison.tex
use more accurate lang

A conditional expectation is taken because \(E\) is designed to be
invariant to different realizations of \(\boldsymbol{X}\). However,
solving this conditional expectation analytically is difficult as
\(\boldsymbol{X}\) can follow almost any distribution. We make an
assumption that \(\boldsymbol{X}\) follows a particular multivariate
normal distribution, and repeatedly draw samples from the given model
\(M\). The estimate of \(E\) is obtained by taking the average of the
\(E_{sample}\) calculated for each sample.

>>>>

A conditional expectation is taken because \(E\) is designed to be
invariant to different realizations of \(\boldsymbol{X}\). However,
solving this conditional expectation analytically is very difficult as
\(\boldsymbol{X}\) can follow arbitrary distributions. Therefore, we
make an assumption that \(\boldsymbol{X}\) follows a particular
multivariate normal distribution

We make an assumption that all the realizations of \(\boldsymbol{X}\)
are generated from a multivariate normal distribution
\(N(\boldsymbol{0}, 0.3^2\boldsymbol{I})\) and then rescaled by the
min-max normalization. The estimate of \(E\) is obtained by taking the
average of the \(E_{sample}\) calculated for samples drawn from the
given model \(M\) repeatedly.
